Target Markdown

### 2024-08-29 _targets.Rmd
Cleaning targets pipeline (removing old code not used)

If you are using old versions of `targets` (<= 0.7.0) and/or `knitr` (<= 1.33), you will need to load the `targets` package in the R Markdown document in order for Target Markdown code chunks to work.

@@

```{targets sem-process}
list(
  tar_target(sim_fw, sim_fw_csc_rerun),
  tar_target(sim_fw_sem,
    sim_fw %>%
      as.data.frame() %>%
      mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae,
            sae_even, cpe_int, cpe_env), log))
    ),
  tar_target(sem_eff,  sem_main_text_eff_csc_rerun),
  tar_target(sem_eff_tab, sem_main_text_eff_tab_csc_rerun),
  tar_target(sem_eff_coeff, sem_main_text_eff_tab_csc_rerun),
  tar_target(sem_collinearity, sem_main_text_collinearity_csc_rerun),
  tar_target(sem_rsquared, sem_main_text_rsquared_csc_rerun),
  tar_target(tab_sem_vif,
    sem_collinearity %>%
      mutate(across(c("response", "Term"), ~var_replacement()[.x])) %>%
      mutate(VIF = round(VIF, 1)) %>%
      select(Response = response, Term, VIF)
    ),
  tar_target(tab_sem_rsquared,
    sem_rsquared %>%
      rename(`$R^2$` = R.squared) %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  ),
  tar_target(tab_sem_simplified_eff,
    sem_simplified_eff_tab %>%
      filter(effect_type == "direct") %>%
      mutate(across(c("response", "predictor"), ~var_replacement()[.x])) %>%
      mutate(effect = round(effect, 2)) %>%
      select(
        Response = response,
        Predictor = predictor,
        `Std estimate` = effect
      )
  ),
  tar_target(tab_sem_doak_eff,
    sem_doak_eff_tab %>%
      filter(effect_type == "direct") %>%
      mutate(across(c("response", "predictor"), ~var_replacement()[.x])) %>%
      mutate(effect = round(effect, 2)) %>%
      select(
        Response = response,
        Predictor = predictor,
        `Std estimate` = effect
      )
  )
)
```

```{r, eval = FALSE}
library(targets)
tar_load_globals()
tar_load(starts_with("sim_fw_csc"))
sim_fw_csc_rerun
sim_fw_csc_rebuild
sim_fw_csc_kno
sim_fw_csc_non_allo
sim_fw_csc_non_allo
tar_read(sem_rsquared) %>%
  rename(`$R^2$` = R.squared) %>%
  kable(caption = "Rsquared for the Structural Equation Model.") %>%
  kable_styling()
```

@@

```{r, eval = FALSE}
tar_load(sem_main_text_tot)
sem_simplified_tot %>%
  select(sim_type, collinearity) %>%
  unnest(cols = c(collinearity)) %>%
  group_by(sim_type) %>%
  summarise(
    med = median(VIF),
    max = max(VIF)
  )
tar_read(sem_main_text_eff_rerun)
tar_load(pred_stab_comp_resp_div)
library(targets)
tar_load(sem_doak_eff_tab_csc_rerun)
sem_doak_eff_tab_csc_rerun %>%
  filter(effect_type == "direct", abs(effect) > .05) %>%
  print(n = 40)

sem_doak_eff_tab_csc_rerun %>%
  filter(effect_type == "direct") %>%
  print(n = 40)
```

@@

## Partial residuals SEM

```{targets partial_sem_relations, eval = FALSE}
list(
  tar_target(scaled_sim_fw_sem,
    sim_fw_sem %>%
      mutate(across(where(is.numeric), ~scale(.x)[, 1]))
    ),
  tar_target(scaled_sem_simplified_model_list,
    map(sem_simplified_model_list,
      ~update(.x, data = scaled_sim_fw_sem)
      )),
  tar_target(scaled_sem_simplified,
    as.psem(scaled_sem_simplified_model_list)
    ),
  tar_target(formula_sem_bivariate_relations,
    c(
      "pop_stab ~ w_avg_tlvl",
      "pop_stab ~ c",
      "pop_stab ~ env_stoch",
      "sae_total ~ richness",
      "sae_total ~ ct_alive",
      "sae_total ~ w_avg_tlvl",
      "sae_total ~ avg_int_strength",
      "cpe ~ avg_int_strength",
      "cpe ~ resp_div"
    )
    )#,
  #tar_target(partial_resid_sem_simplified, {
  #  partialResid(as.formula(formula_sem_bivariate_relations),
  #          modelList = scaled_sem_simplified,
  #          data = scaled_sim_fw_sem
  #        )},
  #        pattern = map(formula_sem_bivariate_relations)
  #),
  #tar_target(sem_simplified_bivariate_relations,
  #  tibble(sem_formula = formula_sem_bivariate_relations) %>%
  #    separate(
  #      col = sem_formula,
  #      into = c("response", "predictor"),
  #      sep = " ~ ", remove = FALSE) %>%
  #  mutate(
  #    data = partial_resid_sem_simplified,
  #    coefs = map2(response, predictor,
  #      ~coefficients(scaled_sem_simplified[[.x]])[c("(Intercept)", .y)]
  #      ),
    #  plot = pmap(list(
    #      data = data,
    #      response = response,
    #      predictor = predictor,
    #      coef = coefs
    #      ),
    #    function (data, response, predictor, coef, ext_data) {
    #      if (predictor %in% c("h", "env_stoch", "resp_div")) {
    #        p <- data %>%
    #          ggplot(aes(
    #              y = yresid, x = xresid,
    #              group = cut(round(xresid, 1),
    #                breaks = length(unique(ext_data[[predictor]]))
    #              )
    #              )) +
    #          geom_boxplot(alpha = .1)
    #      } else {
    #        p <- data %>%
    #          ggplot(aes(y = yresid, x = xresid)) +
    #          geom_point(alpha = .1)
    #      }
    #      p +
    #        geom_abline(
    #          intercept = coef["(Intercept)"],
    #          slope = coef[2],
    #          linewidth = 1
    #          ) +
    #        labs(
    #          x = var_replacement()[predictor],
    #          y = var_replacement()[response]
    #          ) +
    #        coord_cartesian(expand = FALSE) +
    #        theme_half_open()

    #    }, ext_data = scaled_sim_fw_sem)
    #)
  #)
)
```

```{targets p-stab}
list(
  tar_target(p_cpe_env_rho, sim_fw %>%
    ggplot(aes(x = as.factor(1 - rho), y = cpe_env)) +
    geom_hline(yintercept = 1, linetype = "dashed") +
    geom_hline(yintercept = .5, linetype = "dashed", color = "red") +
    geom_boxplot() +
    labs(x = "Response diversity", y = "Env. Compensatory effect") +
    theme_bw()),
  tar_target(p_stoch_pop_stab,
    sim_fw %>%
      ggplot(aes(x = as.factor(env_stoch), y = pop_stab)) +
      geom_boxplot() +
      labs(x = "Environmental stochasticity", y = "Population stability") +
      theme_bw()),
    tar_target(p_stab_comp_stress,
      plot_grid(
        p_cpe_env_rho,
        p_stoch_pop_stab,
        labels = "auto"
      )
    )
)
```

@@

```{targets p_stab_rich_env_rho, tar_simple = TRUE}
sim_fw %>%
  filter(env_stoch %in% c(.1, .6), rho %in% c(0, .75), c == 1, Z == 100) %>%
  ggplot(aes(x = log(richness), y = log(stab_com), color = as.factor(rho))) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm") +
  facet_grid(cols = vars(env_stoch), labeller = label_both) +
  labs(
    x = "Species richness (Log)", y = "Community stability (Log)",
    color = "Environmental correlation"
  ) +
  theme_bw() +
  theme(legend.position = "bottom")
```

## Interaction strength effect

```{targets p_int_stab, tar_simple = TRUE}
sim_fw %>%
  filter(rho %in% c(0), env_stoch == .5) %>%
  pivot_longer(c(stab_com, async, sae_total, cpe,
      sae_even, evenness_sae,
      cpe_int, cpe_env, pop_stab
      ), names_to = "async_decomp", values_to = "values") %>%
  mutate(async_decomp = var_replacement()[async_decomp]) %>%
  ggplot(aes(x = avg_int_strength, y = values)) +
  geom_point() +
  geom_smooth() +
  labs(x = "Avg feeding rate", y = "Asynchrony component") +
  facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
  theme_bw()
```

```{targets p_int_fw, tar_simple = TRUE}
sim_fw %>%
  filter(rho %in% c(0), env_stoch == .5) %>%
  pivot_longer(c(richness, ct_alive, max_tlvl, avg_omnivory, w_avg_tlvl
      ), names_to = "fw_str", values_to = "values") %>%
  mutate(fw_str = var_replacement()[fw_str]) %>%
  ggplot(aes(x = avg_int_strength, y = values)) +
  geom_point() +
  geom_smooth() +
  labs(x = "Avg feeding rate", y = "Food-web structure") +
  facet_wrap(~fw_str, ncol = 3, scales = "free_y") +
  theme_bw()
```

## Avg Omnivory

```{targets p-omn}
list(
  tar_target(p_omn_stab,
    sim_fw %>%
      filter(rho %in% c(0), env_stoch == .5) %>%
      pivot_longer(c(stab_com, pop_stab, async
          ), names_to = "stab_comp", values_to = "values") %>%
      mutate(stab_comp = var_replacement()[stab_comp]) %>%
      ggplot(aes(x = avg_omnivory, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Avg omnivory", y = "Stability component") +
      facet_wrap(~stab_comp, ncol = 3, scales = "free_y") +
      theme_bw()),
  tar_target(p_omn_fw,
    sim_fw %>%
      filter(rho %in% c(0), env_stoch == .5) %>%
      pivot_longer(c(richness, ct_alive, w_avg_tlvl, max_tlvl
          ), names_to = "fw_str", values_to = "values") %>%
      mutate(fw_str = var_replacement()[fw_str]) %>%
      ggplot(aes(x = avg_omnivory, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Avg. Omnivory", y = "Food-web structure") +
      facet_wrap(~fw_str, ncol = 3, scales = "free_y") +
      theme_bw()
  )
)
```

```{targets p-ct-rich-stab}
list(
  tar_target(p_ct_stab,
    sim_fw %>%
      filter(rho %in% c(0), env_stoch == .1) %>%
      pivot_longer(c(stab_com, async, sae_total, cpe,
          sae_even, evenness_sae,
          cpe_int, cpe_env, pop_stab
          ), names_to = "async_decomp", values_to = "values") %>%
      mutate(async_decomp = var_replacement()[async_decomp]) %>%
      ggplot(aes(x = ct_alive, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Connectance", y = "Asynchrony component") +
      facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
      theme_bw()
    ),
  tar_target(p_rich_stab,
    sim_fw %>%
      filter(rho %in% c(0), env_stoch == .1) %>%
      pivot_longer(c(stab_com, async, sae_total, cpe,
          sae_even, evenness_sae,
          cpe_int, cpe_env, pop_stab
          ), names_to = "async_decomp", values_to = "values") %>%
      mutate(async_decomp = var_replacement()[async_decomp]) %>%
      ggplot(aes(x = richness, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Species richness", y = "Asynchrony component") +
      facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
      theme_bw()
    )
)
```

```{targets p_int_fw_str, tar_simple = TRUE}
p1 <- sim_fw %>%
  ggplot(aes(x = as.factor(richness), y = avg_int_strength)) +
  geom_point() +
  labs(x = "Species richness", y = "Avg. Interaction strength") +
  theme_bw()
p2 <- sim_fw %>%
  ggplot(aes(x = as.factor(Z), y = avg_int_strength)) +
  geom_boxplot() +
  labs(x = "PPBR", y = "Avg. Interaction strength") +
  theme_bw()
p3 <- sim_fw %>%
  filter(Z == 100) %>%
  ggplot(aes(x = as.factor(c), y = avg_int_strength)) +
  geom_boxplot() +
  labs(x = "Hill exponent", y = "Avg. Interaction strength") +
  theme_bw()
plot_grid(p1, p2, p3, ncol = 2)
```

@@

```{targets}
list(
  tar_target(sim_param_file, here::here("data", "sim_param_csc_rerun"), format = "file"),
  tar_target(sim_param, {readRDS(sim_param_file)}),
  tar_target(param_comb_nb,
    sim_param %>%
      group_by(Z, rho, env_stoch, c, S) %>%
      summarise(n = n())
  ),
  tar_target(sim_param_tab,
    sim_param %>%
      mutate(resp_div = 1 - rho) %>%
      select(-A) %>%
      pivot_longer(everything(), names_to = "Parameter", values_to = "values") %>%
      group_by(Parameter) %>%
      summarise(
        u = list(sort(unique(values))),
        n = length(unique(round(values, 2))),
        min = min(values),
        max = max(values)
        )
    ),
  tar_target(tab_sim_param,
    sim_param_tab %>%
      mutate(Values = pmap_chr(list(u = u, min = min, max = max, n = n),
          function(u, min, max, n) {
            if (length(u) < 10) {
              out <- paste0("[", paste(round(u, 2), collapse = ", "), "]")
            } else {
              out <- paste0("(", round(min, 2), ", ", round(max, 2), ")", ", N = ", n)
            }
            out
          }
          )) %>%
      filter(!Parameter %in% c("sim_id", "fw_id", "rho", "rep")) %>%
      select(Parameter, Values) %>%
      mutate(
        parameter_name = parameter_name_replacement()[Parameter],
        Parameter = latex_symbol_replacement()[Parameter],
        Parameter = paste0(parameter_name, " (", surround_latex_math(Parameter), ")")
        ) %>%
      select(-parameter_name)
  ),
  tar_target(fix_parameter,
    tibble(
      h = 2,
      B0 = 0.5,
      r = 1.0,
      K = 10,
      alpha_ij = 0.5,
      prod_mass = 1.0
    )
  ),
  tar_target(allometric_parameter,
    tibble(
      d0 = 0.4,
      allo_slope = -0.25,
      ax = list(c(producer = 0, ectotherm = 0.88)), #, endotherm = 0.314
      ay = list(c(producer = 0.0, ectotherm = 4.0)), #, endotherm = 8.0 #not allometric
      eij = list(c(carnivory = 0.85, herbivory = 0.45))
    )
  ),
  tar_target(param_table,
    fix_parameter %>%
  bind_cols(allometric_parameter) %>%
  mutate(across(where(is.list), ~map_chr(.x, function(x) paste_named_vector(x)))) %>%
  mutate(across(where(is.double), ~as.character(.x))) %>%
  pivot_longer(everything(), names_to = "Parameter", values_to = "Values") %>%
  mutate(
    parameter_name = parameter_name_replacement()[Parameter],
    Parameter = latex_symbol_replacement()[Parameter],
    Parameter = paste0(parameter_name, " (", surround_latex_math(Parameter), ")")
    ) %>%
  select(-parameter_name) %>%
  bind_rows(tab_sim_param)
  ),
  tar_target(sim_summary_stat, get_sim_summary_stat(x = sim_fw)),
  tar_target(tab_sim_summary_stat,
  sim_summary_stat %>%
    mutate(
      var = var_replacement()[var],
      type = str_to_sentence(type)
      ) %>%
    select(Type = type, `Metric` = var, N = n, `Median (5%, 95%)`)
  )
)
```

@@

@@

```{r tar-make}
tar_make()
tar_visnetwork()
tar_make_future(workers = 3)
```

>>>>

@@

```{targets sem-process}
list(
  tar_target(sim_fw, sim_fw_csc_rerun),
  tar_target(sim_fw_sem,
    sim_fw %>%
      as.data.frame() %>%
      mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae,
            sae_even, cpe_int, cpe_env), log))
    ),
  tar_target(sem_eff,  sem_main_text_eff_csc_rerun),
  tar_target(sem_eff_tab, sem_main_text_eff_tab_csc_rerun),
  tar_target(sem_eff_coeff, sem_main_text_eff_tab_csc_rerun),
  tar_target(sem_collinearity, sem_main_text_collinearity_csc_rerun),
  tar_target(sem_rsquared, sem_main_text_rsquared_csc_rerun),
  tar_target(tab_sem_vif,
    sem_doak_collinearity_csc_rerun %>%
      mutate(across(c("response", "Term"), ~var_replacement()[.x])) %>%
      mutate(VIF = round(VIF, 1)) %>%
      select(Response = response, Term, VIF)
    ),
  tar_target(tab_sem_rsquared,
    sem_doak_rsquared_csc_rerun %>%
      rename(`$R^2$` = R.squared) %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  ),
  tar_target(tab_sem_simplified_eff,
    sem_simplified_eff_tab %>%
      filter(effect_type == "direct") %>%
      mutate(across(c("response", "predictor"), ~var_replacement()[.x])) %>%
      mutate(effect = round(effect, 2)) %>%
      select(
        Response = response,
        Predictor = predictor,
        `Std estimate` = effect
      )
  ),
  tar_target(tab_sem_doak_eff,
    sem_doak_eff_tab %>%
      filter(effect_type == "direct") %>%
      mutate(across(c("response", "predictor"), ~var_replacement()[.x])) %>%
      mutate(effect = round(effect, 2)) %>%
      select(
        Response = response,
        Predictor = predictor,
        `Std estimate` = effect
      )
  )
)
```

@@

@@

@@

@@

```{targets}
list(
  tar_target(sim_param_file, here::here("data", "sim_param_csc_rerun"), format = "file"),
  tar_target(sim_param, {readRDS(sim_param_file)}),
  tar_target(param_comb_nb,
    sim_param %>%
      group_by(Z, rho, env_stoch, c, S) %>%
      summarise(n = n())
  ),
  tar_target(sim_param_tab,
    sim_param %>%
      mutate(resp_div = 1 - rho) %>%
      select(-A) %>%
      pivot_longer(everything(), names_to = "Parameter", values_to = "values") %>%
      group_by(Parameter) %>%
      summarise(
        u = list(sort(unique(values))),
        n = length(unique(round(values, 2))),
        min = min(values),
        max = max(values)
        )
    ),
  tar_target(tab_sim_param,
    sim_param_tab %>%
      mutate(Values = pmap_chr(list(u = u, min = min, max = max, n = n),
          function(u, min, max, n) {
            if (length(u) < 10) {
              out <- paste0("[", paste(round(u, 2), collapse = ", "), "]")
            } else {
              out <- paste0("(", round(min, 2), ", ", round(max, 2), ")", ", N = ", n)
            }
            out
          }
          )) %>%
      filter(!Parameter %in% c("sim_id", "fw_id", "rho", "rep")) %>%
      select(Parameter, Values) %>%
      mutate(
        parameter_name = parameter_name_replacement()[Parameter],
        Parameter = latex_symbol_replacement()[Parameter],
        Parameter = paste0(parameter_name, " (", surround_latex_math(Parameter), ")")
        ) %>%
      select(-parameter_name)
  ),
  tar_target(fix_parameter,
    tibble(
      h = 2,
      B0 = 0.5,
      r = 1.0,
      K = 10,
      alpha_ij = 0.5,
      prod_mass = 1.0
    )
  ),
  tar_target(allometric_parameter,
    tibble(
      d0 = 0.4,
      allo_slope = -0.25,
      ax = list(c(producer = 0, ectotherm = 0.88)), #, endotherm = 0.314
      ay = list(c(producer = 0.0, ectotherm = 4.0)), #, endotherm = 8.0 #not allometric
      eij = list(c(carnivory = 0.85, herbivory = 0.45))
    )
  ),
  tar_target(param_table,
    fix_parameter %>%
  bind_cols(allometric_parameter) %>%
  mutate(across(where(is.list), ~map_chr(.x, function(x) paste_named_vector(x)))) %>%
  mutate(across(where(is.double), ~as.character(.x))) %>%
  pivot_longer(everything(), names_to = "Parameter", values_to = "Values") %>%
  mutate(
    parameter_name = parameter_name_replacement()[Parameter],
    Parameter = latex_symbol_replacement()[Parameter],
    Parameter = paste0(parameter_name, " (", surround_latex_math(Parameter), ")")
    ) %>%
  select(-parameter_name) %>%
  bind_rows(tab_sim_param)
  ),
  tar_target(sim_summary_stat, get_sim_summary_stat(x = sim_fw)),
  tar_target(tab_sim_summary_stat,
  sim_summary_stat %>%
    ungroup() %>%
    mutate(
      var = recode_factor(var, !!!var_replacement(), .ordered = TRUE),
      type = str_to_sentence(type)
      ) %>%
    select(Type = type, `Metric` = var, N = n, `Median (5%, 95%)`)
  )
)
```

@@

```{targets render, eval = FALSE}
# does not work properly, have to run it by hand
list(
  tar_render(manuscript, here::here("paper","manuscript.Rmd")),
  tar_render(supp, here::here("paper","supplementary_figures.Rmd"))
)
```

@@

```{r tar-make}
tar_make()
```
